Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
removing sol's comment and resolves overflow.

We do not get source locations for failing tests. Doctest solves this.
For Hspec/QuickCheck/HUnit something like JHC's
\verb|SRCLOC_ANNOTATE|
pragma\footnote{%
http://repetae.net/computer/jhc/jhc.shtml} could help.

\begin{quote}
    sol: @kazu should we cite
    \url{http://repetae.net/computer/jhc/jhc.shtml}?
\end{quote}

>>>>

We do not get source locations for failing tests. Doctest solves this.
Something like JHC's
\verb|SRCLOC_ANNOTATE|
pragma\footnote{%
http://repetae.net/computer/jhc/jhc.shtml} could help
for Hspec/QuickCheck/HUnit.
